\documentclass{article}

\author{Latex Guide!}
\title{Lists and Columns}
\date{}

\begin{document}
	\maketitle
	
	\begin{enumerate}
		\item This is the item 1 in Enumerate enviroment.
		\item This is the second one!
	\end{enumerate}

	\begin{itemize}
		\item Bullet type item.
		\item If I add more, they will all be bullets.
	\end{itemize}
	
	\begin{description}
		\item[Step 1:] Cut the onions.
		\item[Step 2:] Add oil.
	\end{description}

\textbf{Nested lists:}

\begin{itemize}
	\item First level in {\tt itemize}
	\begin{enumerate}
		\item First level in {\tt enumerate} (second level globaly)
		\begin{itemize}
			\item Second level in {\tt enumerate}
			(third globaly)
			\begin{enumerate}
				\item Second in {\tt enumerate}
				(fourth globaly)
				\item Second element in fourth level
			\end{enumerate}
			\item Back to third level globaly (second
			in {\tt itemize})
		\end{itemize}
		\item Second level (first one in {\tt enumerate})
	\end{enumerate}
	\item First level
\end{itemize}


\textbf{Default way to enumerate}

\begin{enumerate}
	\item First one.
	\begin{enumerate}
		\item Second one.
		\begin{enumerate}
			\item Third one.
			\begin{enumerate}
				\item Fourth one.
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
\end{enumerate}
	
	\textbf{Changed way}
	
	\renewcommand{\theenumi}{\Roman{enumi}}
	\renewcommand{\labelenumi}{[\textbf{\theenumi}]}
	\renewcommand{\theenumii}{\Alph{enumii}}
	\renewcommand{\labelenumii}{[\textbf{\theenumi}.\textit{\theenumii}]}
\begin{enumerate}
	\item First one.
	\begin{enumerate}
		\item Second one.
		\item Second level again
	\end{enumerate}
	\item First level again
\end{enumerate}

\textbf{Default itemize}

\begin{itemize}
	\item First one.
	\begin{itemize}
		\item Second one.
		\begin{itemize}
			\item Third one.
			\begin{itemize}
				\item Fourth one.
			\end{itemize}
		\end{itemize}
	\end{itemize}
\end{itemize}

\textbf{Itemize changed}
\renewcommand{\labelitemi}{$\circ$}
\renewcommand{\labelitemii}{$\clubsuit$}
\renewcommand{\labelitemiii}{$\diamondsuit$}
\begin{itemize}
	\item First one.
	\begin{itemize}
		\item Second one.
		\begin{itemize}
			\item Third one.	
		\end{itemize}
	\end{itemize}
\end{itemize}
\end{document}